EEG Waveform Analysis of P300 ERP with applications to Brain Computer Interfaces

### 2018-08-29 sensors.tex
Small change

SIFT~\citep{Lowe2004} is a very successful feature extraction technique from Computer Vision .  It has a biomimetic inspiration on how the visual cortex analyze images based on orientations.  This method has been used in \citep{Ramele2016} to analyze EEG signals based on their plots on 2D images.

The first step of the algorithm is plot generation based on single-channel EEG segments $ x(n) $.

@@

\noindent with $\delta$ being the signal magnification factor and $\bar{x}$ and $\sigma_{x}$ the mean and standard deviation of $x$ on the signal segment.  The width of the image is determined straightforward based on the $1$-second length in sample units. This corresponds to the sampling frequency $F_s$ of the EEG signal segment. The width is adjusted by multiplying by a magnification factor $\delta$,

@@

Equation \ref{eq:sift5} determines the height of the image where the signal's zero value will be located.

>>>>

SIFT~\citep{Lowe2004} is a very successful feature extraction technique from Computer Vision .  It has a biomimetic inspiration on how the visual cortex analyze images based on orientations~\citep{cogprints561}.  This method has been used in \citep{Ramele2016} to analyze EEG signals based on their plots on 2D images.

The first step of the algorithm is the plot generation based on single-channel EEG segments $ x(n) $.

@@

\noindent with $\delta$ being the signal magnification factor and $\bar{x}$ and $\sigma_{x}$, the mean and standard deviation of $x$ on the signal segment.  The width of the image is determined based on the $1$-second length size of the segment window in sample units. This corresponds to the sampling frequency $F_s$ of the EEG signal segment. The width is adjusted by multiplying by the magnification factor $\delta$,

@@

Equation \ref{eq:sift5} determines the vertical position of the image where the signal's zero value will be located.
